---
title: "Preliminary 2024 stock assessment of yellowfin tuna in the Indian Ocean"
authors: 
  - name: Name 1
    affiliations:
      - ref: azti
    email: myemail@azti.es
    corresponding: true
  - name: Name 2
    affiliations:
      - ref: azti2
affiliations:
  - id: azti
    name: AZTI, Marine Research, Basque Research and Technology Alliance (BRTA), Txatxarramendi ugartea z/g, 48395 Sukarrieta (Bizkaia), Spain
  - id: azti2
    name: Affiliation 2
toc: true
format:
  html:
    toc-title: 'Contents'
    theme: zephyr
number-sections: true
link-citations: true
bibliography: ../references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      verbose = FALSE,
                      message = FALSE, 
                      warning = FALSE)
```

```{r}
# remotes::install_github("wmoldham/rbbt") # temporarily, until error is fixed
require(knitr)
require(rbbt)
options(knitr.kable.NA = '')
# This will automatically update the BIB file:
keys = rbbt::bbt_detect_citations('report/report.qmd')
bbt_ignore = keys[grepl("fig-|tbl-|eq-|sec-", keys)]
rbbt::bbt_update_bib(path_rmd = 'report/report.qmd', 
                     ignore = bbt_ignore, overwrite = T, translator = "bibtex")
```

{{< pagebreak >}}

# Executive Summary

Make a short summary of the main results and conclusions of this report. This is an example of a reference [@fuPreliminaryIndianYellowfin2021].

# Introduction

Introduction to the report. Some background of previous assessments.

# Background

## Stock structure

Genetic, parasite, and other relevant studies for stock structure.

## Biology

Growth, natural mortality, maturity, etc.

## Fisheries

Describe main fisheries and their contribution to the total catch, etc.

# Data

## Spatial stratification

Describe spatial stratification of the data. Note it do not necessarily need to follow the same stratification in the assessment model.

## Temporal stratification

Time period, seasonal, etc.

## Definition of fisheries

Fisheries that are included in the assessment model.

## Catch

Describe catch per fishery, time series, etc.

## Indices

Describe available indices, methodology for standardization, etc.

## Size data

Describe size data, length bins, catch raising, etc.

## Age data

Describe age-length information, etc.

## Tagging

Tagging information

# Model description

## Population dynamics

Parametrization of recruitment, growth, etc in SS.

## Fishery dynamics

Selectivity principally.

## Tagged fish

Tag reporting, mixing, etc.

## Likelihood components

Weights, error structure, observation error, etc.

## Parameter estimation and uncertainty

Hessian, max gradient, jitter analysis, likelihood profiles, etc.

## Stock status

Related to MSY, depletion trends, Kobe, etc.

# Model runs

## Update from the last assessment

Describe stepwise model developtment, etc.

## Sensitivity and structural uncertainty

Different steepness, M, etc, and spatial configurations.

# Results

## Fits

Describe fits to data.

## Parameter estimates

Describe parameter estimates.

## Time series

Recruitment, SSB, etc.

## Sensitivity

Describe sensitivity analyses.

# Discussion and conclusions

Discuss. Recommendations for future assessments.

# Acknowledgements

Write your acknowledgements.

# Tables

# Figures

# Appendix

## Acronyms and Abbreviations

Include a table with acronyms (e.g., GLMM, SS, etc.)

## Likelihood profiles

## Retrospective analyses

# References {.unnumbered}

::: {#refs}
:::
